formula1

### 2020-06-19 inst/f1points.Rmd
more work

```{r,label=multiplemontecarlotabulation,echo=FALSE}
M3 <- t(apply(OO,1,function(o){tabulate(o+1,nbins=12)}))
dimnames(M3) <- list(system=names(pointslist),correct=0:11)
M3
Mc <- t(apply(M3,1,cumsum))
Mc
Md <- t(apply(M3[,-1],1,cumsum))
colnames(Md) <- paste("<=",colnames(Md),sep="")
Md
```

@@

```{r,label=plotcumulativeM,fig=TRUE}
matplot(t(Mc),type="b",lty=1,pch=16,col=rainbow(nrow(Mc)))
legend("bottomright",lty=1,pch=16,col=rainbow(nrow(Mc)),legend=letters[seq_len(nrow(Mc))])
plot(points_real)
grid()
```

@@

# Discussion and conclusions

>>>>

Have a quick look at the result:

```{r,label=quicklookatOO}
dim(OO)
rownames(OO) <- names(pointslist)
plot(apply(OO,1,mean),ylab='mean number of ranks correct')
```

And more work:

```{r,label=multiplemontecarlotabulation,echo=FALSE}
M3 <- t(apply(OO,1,function(o){tabulate(o+1,nbins=12)}))
dimnames(M3) <- list(system=names(pointslist),correct=0:11)
head(M3)
```

now cumulative:

```{r,label=cummulttab,echo=FALSE}
Md <- t(apply(M3,1,cumsum))
colnames(Md) <- paste("<=",colnames(Md),sep="")
Md
```

@@

```{r,label=plotcumulativeM,fig=TRUE}
plot(Md[,1],ylab='number wrong')
plot(1000-Md[,11],ylab='number perfect')
matplot(t(Md),type="b",lty=1,pch=16,col=rainbow(nrow(Md)))
legend("bottomright",lty=1,pch=16,col=rainbow(nrow(Md)),legend=letters[seq_len(nrow(Md))])
plot(points_real)
grid()
```

@@

Consider the first column of the table above which shows the number of
virtual races in which each scoring system gets the winner incorrect;
a good points system has a low value here.  Note the peculiar finding
that `top3` has by far the lowest number, a finding which I have no
explanation for.

however,
